%! Author = Rémi Jonathan Choquette
%! Date = 2022-11-15

% Preamble
\documentclass[11pt]{article}

% Packages
\usepackage{amsmath}
\usepackage{hyperref}

% Document
\begin{document}
%     This document will highlight the policy for the usage of the Square Credit Card usage for purchase being made by ECA
%     member associations.

    %cover page
    \begin{center}
        \textbf{\LARGE{ECA Square Card Policy}}\\
        \textbf{\large{Version 1.0}}\\
        \textbf{\large{November 15, 2022}}\\
        \textbf{\large{Rémi Jonathan Choquette & Rukhsar Bakhsh}}\\
    \end{center}
    %end of cover page
    %Introduction


    \section{Introduction}

    \subsection{Purpose}
    \begin{enumerate}
        \begin{enumerate}
            \item This document will highlight the policy for the usage of the Square Credit Card usage for purchase being made by ECA
            member associations.
            \item This document will also highlight the policy for the usage of the Square Credit Card usage for purchase being made by ECA.
            \item This document will also highlight the procedure around monthly auditing of card statements.
        \end{enumerate}
    \end{enumerate}

%Policy


    \section{Policy}\label{sec:policy}

    \subsection{ECA Member Associations}\label{subsec:eca-member-associations}
    \begin{enumerate}
        \begin{enumerate}
            \item ECA member associations are allowed to use the Square Credit Card for purchases made on behalf of the association.
            \item ECA member associations are not allowed to use the Square Credit Card for personal purchases.
            \item ECA member associations are not allowed to use the Square Credit Card for purchases made on behalf of other associations.
            \item ECA member associations are not allowed to use the Square Credit Card for purchases made on behalf of ECA.
        \end{enumerate}
    \end{enumerate}

    \subsection{ECA}\label{subsec:eca}
    \begin{enumerate}
        \begin{enumerate}
            \item ECA is allowed to use the Square Credit Card for purchases made on behalf of ECA\@.
            \item ECA is not allowed to use the Square Credit Card for personal purchases.
            \item ECA is not allowed to use the Square Credit Card for purchases made on behalf of other associations.
            \item ECA is not allowed to use the Square Credit Card for purchases made on behalf of ECA member associations.
        \end{enumerate}
    \end{enumerate}

    \subsection{Auditing}\label{subsec:auditing}
    \begin{enumerate}
        \begin{enumerate}
            \item ECA will audit the Square Credit Card statements on a monthly basis.
            \item Member association signatories will be required to provide receipts for all purchases made on behalf of the association.
            \item ECA will provide a quarterly report to the Board of Directors on the usage of the Square Credit Card.
        \end{enumerate}
    \end{enumerate}

    \subsection{Reimbursement}\label{subsec:reimbursement}
    \begin{enumerate}
        \begin{enumerate}
            \item Any receipts that are provided to the ECA through auditing procedures will become invalid for reimbursement.
            \item Any attempt to submit a receipt for reimbursement that has already been submitted to ECA will be rejected and may be considered a violation of the policy.
        \end{enumerate}
    \end{enumerate}

    \subsection{Violations}\label{subsec:violations}
    \begin{enumerate}
        \begin{enumerate}
            \item Any violation of the policy will result in the immediate suspension of the Square Credit Card.
            \item Any violation may be escalated to the Board of Directors for further action, including but not limited to, violating members being placed on the ECA's financial blacklist, and being put on probation.
        \end{enumerate}
    \end{enumerate}
\end{document}